---
title: "Test Cars: Speed and Distance"
author: "Richard Smith and Maria Rodriquez"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.


Revert to the command-line and check your 
git status
You can easily recover from this by a checkout of a branch.
git remote -v # Gives names of remotes 
Fix the headless branch problem 
git branch -f branch-name HEAD # names a branch
git checkout branch-name # switches to a branch 

git push -u origin branch-name

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4
- Bullet 5

## Slide with R Output

```{r cars, echo = TRUE}
dim(cars)
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

